---
title: "Group 1 - Racetrack Times"
subtitle: "Racetrack Variables Presentation"
author: "Troy Tangolics, Colin Birch, Jonah Mackiewicz, Nick Kinstler"
institute: "Marymount University"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
  lib_dir: libs
nature:
  highlightStyle: github
highlightLines: true
countIncrementalSlides: false
---

## Introduction

```{r libraries, message=FALSE, warning=FALSE, paged.print=FALSE}
library(tidyverse)
library(tidymodels)
library(readxl)
library(xaringan)
```

# Modeling Racetrack Times
Research Question- Which car manufacturer produces the fastest track times?

Data- Our data came from the 5 Raceways. These facility use three paddocks
with timing towers, a separate skid pad, and covered tech bays. The track offers multiple course
options with different lengths and routes. Our data is collected through timing towers which
records lap times and also the skid pad which records handling.
---

## Our data

```{r}
Racetrack_data <- read_excel("data/laptimes3.xlsx")
```


```{r first glance, message=FALSE, warning=FALSE, paged.print=FALSE}
names(Racetrack_data)
```
---

## Looking at the data

```{r}
glimpse(Racetrack_data)
```
---

## We are interested in the car type

```{r summary, message=FALSE, warning=FALSE, paged.print=FALSE}
select(Racetrack_data, car)
```
---

## Total amount of cars

```{r car type, message=FALSE, warning=FALSE, paged.print=FALSE}
Racetrack_data %>%
  count(car, sort = TRUE)
```
We were curious how many cars from each manufacturer were listed in the dataset

---

## Times on the tracks

```{r car type 2}
Racetrack_data %>%
  group_by(car) %>%
  summarise(
    min_time = min(Tsukuba_Lap_Time),
    mean_time = mean(Tsukuba_Lap_Time),
    median_time = median(Tsukuba_Lap_Time),
    max_time = max(Tsukuba_Lap_Time)
    )
```
---

## Car Comparison

```{r}
Racetrack_data %>%
  filter(car == "Porsche"| car == "BMW" | car == "Ferrari") %>%
  group_by(car) %>%
  summarise(
    min_time = min(Tsukuba_Lap_Time),
    mean_time = mean(Tsukuba_Lap_Time),
    median_time = median(Tsukuba_Lap_Time),
    max_time = max(Tsukuba_Lap_Time)
    )
```
---

## Modeling Racetrack Times
Research Question- Which car manufacturer produces the fastest track times?

## Racetrack Exploratory Data Anaylsis

We found something interesting was going on over the season. If you look at each of the following graphs, we compared times at later races to the cars first season performance at Tsukuba.
---

## Tusukba Vs. Bedford West

```{r racetrack}
ggplot(data = Racetrack_data,
       mapping = aes(x = Tsukuba_Lap_Time,
                     y = Bedford_West_Circuit_Lap_Time)) +
  geom_point() +
  labs(title = "Tusukba vs. Bedford Comparison",
       subtitle = "Times to complete laps at the respecitve course",
       x = "Tusukba Time (sec)", y = "Bedford Time (sec)")
```
---

## Tusukba Vs. Serres

```{r racetrack 2}
ggplot(data = Racetrack_data,
       mapping = aes(x = Tsukuba_Lap_Time,
                     y = Serres_Circuit_Lap_Time)) +
  geom_point()+
  labs(title = "Tusukba vs. Serres Comparison",
       subtitle = "Times to complete laps at the respecitve course",
       x = "Tusukba Time (sec)", y = "Serres Time (sec)")
```
---

## Tusukba Vs. Hockenheim

```{r racetrack 3, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplot(data = Racetrack_data,
       mapping = aes(x = Tsukuba_Lap_Time,
                     y = Hockenheim)) +
  geom_point()+
  labs(title = "Tusukba vs. Hockenheim Comparison",
       subtitle = "Times to complete laps at the respecitve course",
       x = "Tusukba Time (sec)", y = "Hockenheim Time (sec)")
```
---

## Tusukba Vs. Nordshleife Nurburgring

```{r racetrack 4}
ggplot(data = Racetrack_data,
       mapping = aes(x = Tsukuba_Lap_Time,
                     y = Nordshleife_Nurburgring)) +
  geom_point()+
  labs(title = "Tusukba vs. Nordshleife Comparison",
       subtitle = "Times to complete laps at the respecitve course",
       x = "Tusukba Time (sec)", y = "Nordshleife Time (sec)")
```

```{r subset}
favorites <- Racetrack_data %>%
  filter(car == "Porsche"| car == "BMW" | car == "Ferrari")
```
---

## Favorites

```{r racetrack 5}
ggplot(data = favorites,
       mapping = aes(x = Tsukuba_Lap_Time,
                     y = Nordshleife_Nurburgring,
                     colour = car)) +
  geom_point()+
  labs(title = "Favorites at Tusukba vs. Nordshleife Comparison",
       subtitle = "Favorite Car Types Times to Complete Laps at the Respecitve course",
       x = "Tusukba Time (sec)", y = "Nordshleife Time (sec)")
```
---

## Tusukba Vs. Nordshleife Comparison

```{r racetrack 6}
ggplot(data = Racetrack_data,
       mapping = aes(x = Tsukuba_Lap_Time,
                     y = Nordshleife_Nurburgring,
                     colour = car)) +
  geom_point()+
  labs(title = "Tusukba vs. Nordshleife Comparison",
       x = "Tusukba Time (sec)", y = "Nordshleife Time (sec)")
```
---

## Taking a closer look

This code chunk allowed us to view the cars under a 65 second time at the Tusukba track. 
```{r}
fastest <- Racetrack_data %>%
  filter(Tsukuba_Lap_Time < 65)
```
---

## Tusukba Vs. Nordshleife Comparison 

```{r racetrack 7}
ggplot(data = fastest,
       mapping = aes(x = Tsukuba_Lap_Time,
                     y = Nordshleife_Nurburgring,
                     colour = car)) +
  geom_point()+
  labs(title = "Tusukba vs. Nordshleife Comparison",
       x = "Tusukba Time (sec)", y = "Nordshleife Time (sec)")
```

```{r}
morefastest <- Racetrack_data %>%
  filter(Tsukuba_Lap_Time < 60.5)
```
---

```{r racetrack 8}
ggplot(data = morefastest,
       mapping = aes(x = Tsukuba_Lap_Time,
                     y = Nordshleife_Nurburgring,
                     colour = car)) +
  geom_point()+
  labs(title = "Tusukba vs. Nordshleife Comparison",
       x = "Tusukba Time (sec)", y = "Nordshleife Time (sec)")
```



