---
title: "Group 1 - Racetrack Times"
subtitle: "Racetrack Variables Presentation"
author: "Troy Tangolics, Colin Birch, Jonah Mackiewicz, Nick Kinstler"
institute: "Marymount University"
date: "`r Sys.Date()`"
output:
 xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

# Modeling Racetrack Times
Research Question- Which car manufacturer produces the fastest track times?

Data- Our data came from the Virginia International Raceway. This facility uses three paddocks
with timing towers, a separate skid pad, and covered tech bays. The track offers multiple course
options with different lengths and routes. Our data is collected through timing towers which
records lap times and also the skid pad which records handling.
---

# R Code

```{r comment='#'}
# a boring regression
fit = lm(dist ~ 1 + speed, data = cars)
coef(summary(fit))
```

---

# R Plots

```{r cars, fig.height=4}
par(mar = c(4, 4, 1, .1))
plot(cars, pch = 19, col = 'darkgray', las = 1)
abline(fit, lwd = 2)
```